Optical Detection of Paramagnetic Defects in a CVD-grown diamond\\-- Supplementary Material

### 2021-03-12 Mes papiers/CR-CVD/SI/CVD_para_SI.tex

The NV$^-$ photoluminescence as a function of the magnetic field amplitude that is presented in the Fig. 3 of the main text was realized on a CVD-grown sample. 
We also performed similar scans on several samples grown via the High-Pressure-High-Temperature (HPHT) method. 
Fig. \ref{fig1SI} shows a scan realized on HPHT samples that have been irradiated in order to increase the NV yield. 
The sample we use in Fig. \ref{fig1SI} is a Ib electron irradiated HPHT diamond crystal with a NV concentration expected to be in the 5-20 ppm range.
The PL feature that can be observed at 20G was also observed in the CVD-grown samples. We attributed it to the resonant dipolar interaction between a standard polarized NV center and one NV strongly coupled to the nuclear spin of a $^{13}$C atom sitting one shell away.
Notably, no other features could be detected at larger magnetic field values. We realized such scans on many different highly-doped HPHT samples and, systematically, no CR features are observed at 50 and 122 G.

@@

\section{Fitting of the cross-relaxation scans}
\begin{figure}
\includegraphics[scale=0.5]{Gauss_vs_Lor_VH}
\caption{Zoom-in on the VH$^-$ cross-relaxation line from Fig.3 of the main text with Gaussian (orange,plain line) and Lorentzian (red, dashed line) fit}
\label{Gauss_vs_Lor}
\end{figure}
In order to extract quantitative information from Fig.3 of the main text, we had ta apply two distinct fits to the raw data : first a polynomial fit to subtract the slowly decaying PL due to sate-mixing, then a Lorentzian fit on the VH$^-$ and WAR1 resonance lines to measure the central position, width and amplitude of the lines.

For the subtracting fit, we chose a polynomial fit because numerical solving of the transverse-field dependent spin depolarization could not properly fit our results. We had to use up a 4th order polynomial in order to obtain a tight fit to the data. Higher order polynomials did not significantly change the fitting envelope.

The second and third peaks were fitted better on their wings by a Gaussian than by a Lorentzian lineshape, as can be seen in Fig. \ref{Gauss_vs_Lor} where the Gaussian fit yields a $R^2=0.983$ greater than the $R^2=0.974$ from the Lorentzian fit. This is coherent with the fact that the inhomogeneous broadening of the various spin species dominates the coupling strength between the spins.

\section{Sample fabrication details}
The main CVD sample of this study is presented in thorough details in \citep{TALLAIRE2020421}. It is a thick (100) oriented diamond grown in-house by CVD with an initial concentration [N]$\approx$25~ppm and separated from its HPHT substrate. It was electron irradiated at 10MeV and a fluence of $2\cdot 10^{18}$~cm$^{-2}$ and in situ annealed at 900°C during irradiation to give a final concentration [NV]$\approx$4.6~ppm.

The HPHT sample used in Sec.I of the supplementary material is a thick (111)-oriented diamond from Sumitomo and was electron irradiated at an energy of 2 MeV and a fluence of $7\cdot 10^{18}$~cm$^{-2}$. It was then annealed in vacuum for 2h at 950°C.

@@

\bibitem{jiang2018estimation}
Feng-Jian Jiang, Jian-Feng Ye, Zheng Jiao, Zhi-Yong Huang, and Hai-Jiang Lv.
\newblock Estimation of vector static magnetic field by a nitrogen-vacancy
  center with a single first-shell 13c nuclear (nv--13c) spin in diamond.
\newblock {\em Chinese Physics B}, 27(5):057601, 2018.

@@

\bibitem{alvarez_local_2015}
Gonzalo~A. Álvarez, Christian~O. Bretschneider, Ran Fischer, Paz London, Hisao
  Kanda, Shinobu Onoda, Junichi Isoya, David Gershoni, and Lucio Frydman.
\newblock Local and bulk {13C} hyperpolarization in nitrogen-vacancy-centred
  diamonds at variable fields and orientations.
\newblock {\em Nat Commun}, 6(1):8456, December 2015.

>>>>

The NV$^-$ photoluminescence as a function of the magnetic field amplitude that is presented in the Fig. 3 of the main text was realized on a CVD-grown sample. 
We also performed similar scans on several samples grown via the High-Pressure-High-Temperature (HPHT) method. 
Fig. \ref{fig1SI} shows a scan realized on HPHT samples that have been irradiated in order to increase the NV yield. 
The sample we use for the results shown in Fig. \ref{fig1SI} is a Ib electron irradiated HPHT diamond crystal with a NV concentration expected to be in the 5-20 ppm range.
The PL feature that can be observed at 20G was also observed in the CVD-grown samples. We attributed it to the resonant dipolar interaction between a polarized NV center and one NV strongly coupled to the nuclear spin of a $^{13}$C atom sitting one shell away.
Notably, no other features could be detected at larger magnetic field values. We realized such scans on many different highly-doped HPHT samples and, systematically, no CR features are observed at 50 and 122 G.

@@

\section{Fit of the cross-relaxation features}
\begin{figure}
\includegraphics[scale=0.5]{Gauss_vs_Lor_VH}
\caption{Zoom-in on the VH$^-$ cross-relaxation line from Fig.3 of the main text with Gaussian (orange,plain line) and Lorentzian (red, dashed line) fit}
\label{Gauss_vs_Lor}
\end{figure}
In order to extract quantitative information from Fig.3 of the main text, we apply two distinct fits to the raw data : first we employ a polynomial fit to subtract the slowly decaying PL due to state-mixing, then we use a Lorentzian fit on the VH$^-$ and WAR1 resonance lines to measure the central position, the width and the contrast of the features.

We chose a polynomial fit in Fig. 3 because numerical solving of the transverse-field dependent spin depolarization with the 7 levels of the NV centers could not properly fit our results. We had to go until a 4th order polynomial in order to obtain a tight fit to the data. Higher order polynomials did not significantly change the fitting envelope.

The second and third peaks were fitted better when using a Gaussian rather by a Lorentzian lineshape, as can be seen in Fig. \ref{Gauss_vs_Lor} where the Gaussian fit yields a $R^2=0.983$ greater than the $R^2=0.974$ from the Lorentzian fit (the difference is best seen on their wings). This is consistent with the fact that the inhomogeneous broadening of the various spin species dominates the coupling strength between the spins.

\section{Sample fabrication details}
The main CVD sample of this study is presented in thorough details in \citep{TALLAIRE2020421}. It is a thick (100) oriented diamond grown in-house by CVD with an initial concentration [N]$\approx$25~ppm and separated from its HPHT substrate. It was electron irradiated at 10MeV and a fluence of $2\cdot 10^{18}$~cm$^{-2}$ and in situ annealed at 900$^\circ$C during irradiation to give a final concentration [NV]$\approx$4.6~ppm.

The HPHT sample used in Sec.I of the supplementary material is a thick (111)-oriented diamond from Sumitomo and was electron irradiated at an energy of 2 MeV and a fluence of $7\cdot 10^{18}$~cm$^{-2}$. It was then annealed in vacuum for 2h at 950$^\circ$C.

@@

\bibitem{jiang2018estimation}
Feng-Jian Jiang, Jian-Feng Ye, Zheng Jiao, Zhi-Yong Huang, and Hai-Jiang Lv.
\newblock Estimation of vector static magnetic field by a nitrogen-vacancy
  center with a single first-shell 13c nuclear (nv--13c) spin in diamond.\newblock {\em Chinese Physics B}, 27(5):057601, 2018.

@@

\bibitem{alvarez_local_2015}
Gonzalo~A. Álvarez, Christian~O. Bretschneider, Ran Fischer, Paz London, Hisao
  Kanda, Shinobu Onoda, Junichi Isoya, David Gershoni, and Lucio Frydman.\newblock Local and bulk {13C} hyperpolarization in nitrogen-vacancy-centred
  diamonds at variable fields and orientations.
\newblock {\em Nat Commun}, 6(1):8456, December 2015.
